### 2021-02-15 background.tex
Taint analysis in background

L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot. This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect 75.49\% of malicious behavior explored ($77$ among $102$). However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps \kn{The last bit requires further extrapolation. The way it was explained to me is not evident here. Especially the "interference of static analysis" requires expansion something in the lines of "The papers did not explore what happens when an existing static analysis in the background is removed, and how much of the analysis results actually come from existing static analysis"}.

>>>>

L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot. This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect 75.49\% of malicious behavior explored ($77$ among $102$). However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps

Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet. Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}. Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system. Flowdroid~\cite{arzt:pldi-2014} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis. Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.
